### 2023-07-25 observingCarbonCycle.qmd
corrections following reviews

From the data we feed models with to uncertainties caused by missing or poorly understood processes, current BCP models still disagree on the estimation of carbon export both currently and in response to climate change [@Henson2022-hg]. However, the ongoing increase in deployments of autonomous platforms and the development of new sensors is providing new opportunities to enhance the parametrization of key biogeochemical processes to better estimate carbon export and sequestration.

@@

In all, POC fluxes derived from sediment traps and $^{234}Th$ have their own uncertainties and errors thus their estimations of downward POC fluxes should not be seen as ground truth. In addition, they are labor-intensive and require ship support. Their relative contribution to the estimation of POC fluxes is thus expected to keep decreasing (@fig-sediment-trap-thorium-yearly-distribution) with the advent of alternative new methods promoted by an increasing use of automated underwater vehicles (AUVs).

@@

It is admitted that ship-based measurements are potentially the most precise. However, they lack spatiotemporal coverage and they are usually not cost-effective. Consequently, oceanographers have turned to new platforms and have developed new sensors to study the marine carbon cycle and the BCP in particular.

@@

In order to fill the scarcity of data from research vessels and moorings as well as coping with surface-constrained satellite measurements, AUVs have been developed to take in situ measurements in all weathers and at all times, only being dependent on their battery life and ocean currents (for drifting AUVs).

Biogeochemical-Argo (BGC-Argo) profiling floats (@fig-bgc-float) are probably the most well known AUVs to study the BCP. They are cost-effective, able to monitor biogeochemical processes at a global scale throughout the year and under all weather conditions [@Chai2020-uq]. The goal of the BGC-Argo community is to develop an array of 1000 floats that measure 6 key biogeochemical and bio-optical variables: Chlorophyll a (Chla), particle backscatter ($b_{bp}$), oxygen, nitrate, pH and downwelling irradiance in addition to temperature and salinity [@Roemmich2019-pn]. Besides this objective, the BGC-Argo community is testing new sensors (see @sec-BGC-sensors) to explore specific topics related to the BCP [@Claustre2020-jo].

Gliders are also effective AUVs to study the BCP [e.g. @Omand2015-mf]. In comparison with BGC-Argo floats (@fig-BGC-Argo-cycle), gliders mostly operate in shallow waters [@Chai2020-uq] and are able to take measurements along a predefined transect due to their ability to change their internal weight distribution [@Johnson2009-kb].

@@

The BGC-Argo array has already demonstrated its ability to understand some aspects of the BCP [e.g. @Lacour2017-ro; @Lacour2019-id; @Briggs2020-gz; @Yang2021-vg; @Llort2018-pa; @Wang2022-hn]. However, the current array may lack some key data to further our understanding of the BCP. Therefore, other types of sensors could be added to help fill this gap.

@@

```{r, OST on BGC-Argo example with jump}
#| label: fig-estapa-method
#| fig-cap: Application of the method of @Estapa2023-oz on a drifting transmissometer to divide the $c_{p}$ signal into a continuous (dark blue) component, cleaned from spikes and negative jumps (assumed as not related to carbon flux) and a discontinuous (positive jumps, light blue) component. Data from BGC-ARGO float WMO 4903634, drifting at 1000 m during its 9$^{th}$ cycle.
library(tidyverse)
library(ggplot2)
library(vroom)
#library(castr)
library(plyr)
library(scales)
library(lubridate)
library(latex2exp)

@@

```{=latex}
\newpage
```

The UVP6 (@fig-UVP6) is a miniaturized version of the UVP5 [@Picheral2021-sx], an imaging system developed to characterize particles (e.g. size, gray level, taxonomic group). Two versions of the UVP6 are available: the UVP6-HF (high frequency) and the UVP6-LP (low power) which has been specifically designed for AUVs that have strict energy requirements (e.g. autonomous floats).

@@

```{=latex}
\newpage
```

The UVP6-LP (hereafter referred to as UVP6) is thus both a particle counter (0.1 mm - 2.5 mm) and a particle classifier (\> 0.6 mm). The former counts particles in different size classes in order to compute the PSD while the latter extracts pixel-related and geometric features from each image to classify them (i.e. assign them a taxonomic group) directly on board using artificial intelligence (@sec-uvp6) with the aim of estimating zooplankton biomass [@Claustre2020-jo; @Claustre2021-tx].

The deployment of autonomous platforms equipped with a UVP6 and the zooplankton recognition algorithm for the study of the BCP is just beginning (first deployment in May 2022 in the Labrador Sea, see @sec-case-study-labrador-sea). On the contrary, the use of PSD in carbon flux studies has already been thoroughly explored [@Guidi2008-vp; @Iversen2010-an; @Jouandet2011-bt; @McDonnell2012-ic; @Roullier2014-wf; @Guidi2015-sj; @Guidi2016-nj; @Ramondenc2016-nu; @Kiko2017-qy; @Fender2019-ou; @Giering2020-mc; @Cael2021-qn; @Bisson2022-bt].

@@

The assumption that all particles of a given size class have the same carbon content and settling rate questions the formulation of the model itself (@eq-carbon-flux-finite). It has been shown that the pool of sinking particles is varied (e.g. compact fecal pellets, porous aggregates) and that the main driver of the sinking speed is currently subject to debate [@sec-sinking-speed]. Therefore, the size-dependent model of @Guidi2008-vp could be improved by taking into account the composition and nature of particles and by increasing the number of paired measurements between UVP PSD-derived flux estimations and other direct POC flux estimations (e.g. sediment traps, $^{234}Th$, OST).

@@

1.  BGC-Argo floats equipped with a UVP6 and the zooplankton recognition algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires special attention to the energy consumption of each sensor. In @sec-uvp6, I will therefore describe the methodology used to develop the zooplankton classification model for the UVP6 accounting for energy limitations.
2.  Four BGC-Argo floats equipped with both an OST and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to study the dynamics of carbon fluxes and particle concentrations. In this chapter, I will explore the seasonality of the latter and compare how the two sensors relate as two independent measurements of particle and carbon fluxes.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1,000 m). In @sec-bcp-sequestration, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.

>>>>

Current BCP models still disagree on the estimation of the actual carbon export and its response to climate change [@Henson2022-hg]. However, the ongoing increase in deployments of autonomous platforms and the development of new sensors is providing new opportunities to enhance the parametrization of key biogeochemical processes to reduce uncertainties and better estimate carbon export and sequestration.

@@

In all, POC fluxes derived from sediment traps and $^{234}Th$ have their own uncertainties and errors thus their estimates of downward POC fluxes should not be seen as ground truth. In addition, they are labor-intensive and require ship support. Their relative contribution to the estimation of POC fluxes is thus expected to keep decreasing (@fig-sediment-trap-thorium-yearly-distribution) with the advent of alternative methods promoted by an increasing use of autonomous underwater vehicles (AUVs). However, the AUV-derived estimates have also their own caveats (see @sec-BGC-sensors) therefore traditional methods to measure POC fluxes will still be needed to calibrate those from autonomous vehicles.

@@

It is admitted that ship-based or fixed-point (e.g. moorings) measurements are potentially the most precise. However, they lack spatiotemporal coverage and they are usually not cost-effective. Consequently, oceanographers have turned to new platforms and have developed new sensors to study the marine carbon cycle and the BCP in particular.

@@

In order to fill the scarcity of data from research vessels and moorings as well as coping with surface-constrained satellite measurements, AUVs have been developed to make in situ measurements in all weather conditions and seasons and at all times, only being dependent on their battery life and ocean currents (for drifting AUVs).

Biogeochemical-Argo (BGC-Argo) profiling floats (@fig-bgc-float) are probably the best known platforms to study the BCP. They are cost-effective, able to monitor biogeochemical processes at a global scale throughout the year and under all weather conditions [@Chai2020-uq]. The goal of the BGC-Argo community is to develop an array of 1000 floats that measure 6 key biogeochemical and bio-optical variables: Chlorophyll a (Chla), particle backscatter ($b_{bp}$), oxygen, nitrate, pH and downwelling irradiance in addition to temperature and salinity [@Roemmich2019-pn]. Besides this objective, the BGC-Argo community is testing new sensors (see @sec-BGC-sensors) to explore specific topics related to the BCP [@Claustre2020-jo].

Gliders are also effective platforms to study the BCP [e.g. @Omand2015-mf]. In comparison with BGC-Argo floats (@fig-BGC-Argo-cycle), gliders mostly operate in shallow waters [@Chai2020-uq] and are able to take measurements along a predefined transect due to their ability to change their internal weight distribution [@Johnson2009-kb].

@@

The BGC-Argo array has already demonstrated its ability to investigate some aspects of the BCP [e.g. @Lacour2017-ro; @Lacour2019-id; @Briggs2020-gz; @Yang2021-vg; @Llort2018-pa; @Wang2022-hn]. However, the current array may lack some key data to further our understanding of the BCP. Therefore, other types of sensors are being added to help fill this gap.

@@

```{r, OST on BGC-Argo example with jump}
#| label: fig-estapa-method
#| fig-cap: Application of the method of @Estapa2017-jr on a drifting transmissometer to divide the $c_{p}$ signal into a continuous (dark blue) component, cleaned from spikes and negative jumps (assumed as not related to carbon flux) and a discontinuous (positive jumps, light blue) component. Data from BGC-ARGO float WMO 4903634, drifting at 1000 m during its 9$^{th}$ cycle.
library(tidyverse)
library(ggplot2)
library(vroom)
#library(castr)
library(plyr)
library(scales)
library(lubridate)
library(latex2exp)

@@

```{=latex}
\newpage
```
The UVP6 (@fig-UVP6) is a miniaturized version of the UVP5 [@Picheral2021-sx], an imaging system developed to characterize particles (e.g. size, gray level, taxonomic group). Two versions of the UVP6 are available: the UVP6-HF (high frequency), and the UVP6-LP (low power) which has been specifically designed for AUVs that have strict energy requirements (e.g. autonomous floats).

@@

```{=latex}
\newpage
```
The UVP6-LP (hereafter referred to as UVP6) is thus both a particle counter for particles in the 0.1 - 2.5 mm size range and a particle classifier (\> 0.6 mm). The former counts particles in different size classes in order to compute the PSD while the latter extracts pixel-related and geometric features from each image to classify them (i.e. assign them a taxonomic group) directly on board using artificial intelligence (@sec-uvp6) with the aim of estimating zooplankton biomass [@Claustre2020-jo; @Claustre2021-tx].

The deployment of autonomous platforms equipped with a UVP6 and a zooplankton classification algorithm for the study of the BCP is just beginning (first deployment in May 2022 in the Labrador Sea, see @sec-case-study-labrador-sea). On the contrary, PSDs in carbon flux studies have been extensively used [@Guidi2008-vp; @Iversen2010-an; @Jouandet2011-bt; @McDonnell2012-ic; @Roullier2014-wf; @Guidi2015-sj; @Guidi2016-nj; @Ramondenc2016-nu; @Kiko2017-qy; @Fender2019-ou; @Giering2020-mc; @Cael2021-qn; @Bisson2022-bt].

@@

The assumption that all particles of a given size class have the same carbon content and settling rate questions the formulation of the model itself (@eq-carbon-flux-finite). It has been shown [@Durkin2021-nq] that the pool of sinking particles is varied (e.g. compact fecal pellets, porous aggregates) and that the main driver of the sinking speed is currently subject to debate [@sec-sinking-speed]. Therefore, the size-dependent model of @Guidi2008-vp could be improved by taking into account the composition and nature of particles [@Durkin2021-nq] and by increasing the number of paired measurements between UVP PSD-derived flux estimates and other direct POC flux estimates (e.g. sediment traps, $^{234}Th$, OST).

@@

1.  BGC-Argo floats equipped with a UVP6 and a zooplankton classification algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires to minimize the energy consumption of each sensor. In @sec-uvp6, I will therefore describe the methodology used to develop a zooplankton classification model for the UVP6 accounting for energy limitations.
2.  Four BGC-Argo floats equipped with both an OST and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to study the dynamics of carbon fluxes and particle concentrations. In this chapter, I will explore the seasonality of the latter and compare how the two sensors relate as two independent measurements of particle and carbon fluxes.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1,000 m). In @sec-bcp-sequestration, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.

### 2023-07-25 uvp6_part.qmd
corrections following reviews

```{r, confusion matrix N detritus, fig.height=4, fig.width=6}
#| label: fig-confusion-matrix-final-model
#| fig-cap: Confusion matrix (normalized on true labels) of the final UVP6 model trained with XGBoost.

>>>>

```{r, confusion matrix UVP6, fig.height=4, fig.width=6}
#| label: fig-confusion-matrix-final-model
#| fig-cap: Confusion matrix (normalized on true labels) of the final UVP6 model trained with XGBoost.
